Determinants of Soccer Players' Market Values in Major European League(s)

### 2024-11-29 paper/paper.qmd
Updated Title and Abstract of the paper

---
title: "Determinants of Soccer Players' Market Values in Major European League(s)"
subtitle: "A Comparative Linear Regression Analysis Across Five Leagues"
author: 
  - John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
abstract: ""
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Introduction{#sec-intro}
Certainly! Here's an updated introduction that explicitly mentions all the packages from the references you provided and integrates their relevance to the study:

@@

@@

![Example to Get Club Ranking Data](../other/photos/Club_Ranking.png){#fig-club_ranking}
## Data Cleaning

>>>>

---
title: "Determinants of Soccer Players' Market Values in Major European League(s)"
subtitle: "Goals, Assists, and Age Dominate, While League-Specific Patterns Add Complexity"
author: 
  - John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
abstract: "The global soccer transfer market is shaped by diverse factors influencing player valuations across leagues. This study analyzes determinants of market value in five major European leagues using data from the 2023/24 season. Goals and assists consistently emerge as the strongest predictors, with the Premier League valuing goals highest and the Bundesliga emphasizing assists, while age negatively affects value across all leagues, particularly in La Liga. These insights highlight universal trends and league-specific valuation dynamics, offering actionable guidance for clubs, agents, and analysts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Introduction{#sec-intro}

@@

The estimand in this study is the expected market value of a soccer player as a function of performance metrics (e.g., goals, assists), contextual variables (e.g., club and national team rankings), and demographic factors (e.g., age, position), while accounting for league-specific differences. This estimand represents a linear relationship between player attributes and market value, enabling a comparison of the impact of various predictors across leagues.

@@

![Example to Get Club Ranking Data](../other/photos/Club_Ranking.png){#fig-club_ranking}

## Data Cleaning
